How to compute the fusion product of MV cycles in type A

### 2021-04-14 draft.tex

% Dimensions: $(1,0,-1)$ for both.

@@

% \begin{example}
% Let $G = SL_3$ and consider the following tableaux:
% $$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$

% Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.

% Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.

% The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
% The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
% Then we are considering the following matrix:
% \[
% X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
%     0 & 1 & & & & & & & & & & \\
%      & 0 & 1 & & & & & & & & & \\
%      & & 0 & 1 & & & & & & & & \\
%      & & & 0 & 1 & & & & & & & \\
%      & & & & 0 & 1 & & & & & & \\
%      & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
%      & & & & & & 0 & 1 & & & & \\
%      & & & & & & & 0 & 1 & & & \\
%      & & & & & & & & 0 & 1 & & \\
%      & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
%      & & & & & & & & & & 0 & 1 \\
%      & & & & & & & & & & -s^2 & 2s
% \end{BMAT}
% \right].
% \]
% By computer, it can be checked that we obtain the following 3 ideals:
% $$
% \begin{array}{cl}
%     I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
%     I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
%     I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
% \end{array}
% $$
% It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same. The tableau corresponding to each ideal is
% $$
% \begin{array}{cccc}\vspace{1mm}
%     \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
%     \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
%     \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
% \end{array}
% $$
% The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
% \end{example}

\begin{example}
Let $G = \GL_3$. Consider the tableaux
$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
     & & 0 & 1 & & \\
     & & & 0 & A_{23}^1 & A_{23}^2 \\
     & & & & 0 & 1 \\
     & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
Using a computer, the ideals we get are
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
\end{array}
$$
The tableaux corresponding to each ideal is
$$
\begin{array}{cc}\vspace{1mm}
    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
    \young(1123,23) & \text{for } I_3
\end{array}
$$
and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
\end{example}

>>>>

\acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$. So far so good. However, the ``smallest'' ``fission'' of $\tau$ is $\young(112,23) , \young(3)$. We could define ``smallest'' to mean minimizing the dimension of the generalized $s$-eigenspace. What do you guys think? If we agree to do this we should amend this example. For Joel: this is an example where our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley (quoted in my thesis). They would get $\lambda = (3,1)$. I think that their map satisfies $\lambda$ dominant and $\mu$ such that each $\mu_i\ge 1$.}

Dimensions: $(1,0,-1)$ for both.

@@

\begin{comment}
\begin{example}
Let $G = SL_3$ and consider the following tableaux:
$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$

Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.

Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.

The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
Then we are considering the following matrix:
\[
X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
    0 & 1 & & & & & & & & & & \\
     & 0 & 1 & & & & & & & & & \\
     & & 0 & 1 & & & & & & & & \\
     & & & 0 & 1 & & & & & & & \\
     & & & & 0 & 1 & & & & & & \\
     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
     & & & & & & 0 & 1 & & & & \\
     & & & & & & & 0 & 1 & & & \\
     & & & & & & & & 0 & 1 & & \\
     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
     & & & & & & & & & & 0 & 1 \\
     & & & & & & & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
By computer, it can be checked that we obtain the following 3 ideals:
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
\end{array}
$$
It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same. The tableau corresponding to each ideal is
$$
\begin{array}{cccc}\vspace{1mm}
    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
\end{array}
$$
The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
\end{example}
\end{comment}

\begin{example}

    \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{mirkovic2007quiver}.}

Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
     & & 0 & 1 & & \\
     & & & 0 & A_{23}^1 & A_{23}^2 \\
     & & & & 0 & 1 \\
     & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
Using a computer, the ideals we get are
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
\end{array}
$$
The tableaux corresponding to each ideal is
$$
\begin{array}{cc}\vspace{1mm}
    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
    \young(1123,23) & \text{for } I_3
\end{array}
$$
and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
\end{example}
